Parallelization of Push-based System for Molecular Simulation Data Analysis with GPU

### 2016-01-27 paper/paperSource.tex
paper changes

\subsection{Contribution and roadmap of the paper} 
The proposed improved version of push-based system for molecular simulation data analysis, we believe, gives an opportunity for scientists to run their analysis even faster now. Taking an advantage of GPU devices nature and incorporating parallelism and streaming for different types of queries, we have come up with a good speed up over sequential processing, which already had a good speed up in terms of performance in comparison with original pull-based approach. Since in this paper we don't expect certain form of data, we have come up with a tool that generates mock data for any number of atoms and frames, which can be used for performance tests that were done consequently, too. This mock data has exactly the same information that would come with Gromacs simulation files, and it has exactly the same format as in the previous paper \cite{mainPaper} right before loading it to memory. This improved version has been developed on Amazon Elastic GPU nodes that consequently can be replicated and scaled up becoming more of a streaming processing engine, which can be very effective on costs, since it is always easy to scale up the nodes, shut them down and spin them back up as well as on a simple desktop computer with a GPU device.

The major technical contributions presented here are:
\begin{itemize}
\item Design the network (tree like) of the most commonly used queries in MS (physics);
\item Build the system: design and build the modules, representing the quantities to be
computed in an efficient manner, following the already built
network;
\item Develop a scientific simulation database benchmark that can be used for evaluating similar systems and products.
\end{itemize}

The remainder of this paper is arranged as follows: in Section
\ref{sc:relatedwork} we give a survey of the systems used in the
field of MS systems analysis. We continue the paper with Section
\ref{sc:querynetwork} in which we show the design of the query
network build from the most widely used quantities in MS system
analysis. In Section \ref{sc:system} we describe our push-based
system for MS data analysis. Then, in Section \ref{sc:experiments}
we present the benchmark designed to test our system as well as the
results attained through comprehensive experiments run on real MS
generated data. At the end, we conclude this paper with Section
\ref{sc:conclusion} in which we give an overview of our possible
future endeavors in the field of MS data analysis.

>>>>

\subsection{Contribution and roadmap of the paper} 
The proposed improved version of push-based system for molecular simulation data analysis, we believe, gives an opportunity for scientists to run their analysis even faster now. Taking an advantage of GPU devices nature and incorporating parallelism and streaming for different types of queries, we have come up with a good speed up over sequential processing, which already had a good speed up in terms of performance in comparison with original pull-based approach. Since in this paper we don't expect certain form of data, we have come up with a tool that generates mock data for any number of atoms and frames, which can be used for performance tests that were done consequently, too. This mock data has exactly the same information that would come with Gromacs simulation files, and it has exactly the same format as in the previous paper \cite{mainPaper} right before loading it to memory. This improved version has been developed on Amazon Elastic GPU \cite{amazonGPU} nodes that consequently can be replicated and scaled up becoming more of a streaming distributed processing engine (which can be very effective on costs, since it is always easy to scale them up, shut them down and spin them back up), as well as on a simple desktop computer with a GPU device.
In general, major contribution of this paper is the framework of push-based system with an incorporated parallelism based on CUDA programming language. Besides it, there was developed a tool which generates mockup data of the same format as of the real MS simulations and represent a python script with arguments given as number of frames and atoms.

The structure of the framework which will be described later is developed in such a way that one can easily add new queries based on their complexity or modify existing ones adding appropriate selections and filters.
